---
title: "Analysis"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Abstract

Immigration is one of the most widely debated issues today. It has, therefore, also become an important issue in party competition, and radical right parties are trying to exploit the issue. This opens up many pressing questions for researchers. To answer these questions, data on the self-ascribed and unified party positions on immigration and immigrant integration issues is needed. So far, researchers have relied on expert survey data, media analysis data and ‘proxy’ categories from the Manifesto Project Dataset. However, the former two only give the mediated party position, and the latter relies on proxies that do not specifically measure immigration. The new dataset presented in this article provides researchers with party positions and saliency estimates on two issue dimensions – immigration and immigrant integration – in 14 countries and 43 elections. Deriving the data from manifestos enables the provision of parties’ unified and unfiltered immigration positions for countries and time points not covered in expert surveys and media studies, making it possible to link immigration and immigrant integration positions and saliency scores to other issue areas covered in the Manifesto Project Dataset. Well-established criteria are used to distinguish between statements on (1) immigration control and (2) immigrant integration. This allows for a more fine-grained analysis along these two dimensions. Furthermore, the dataset has been generated using the new method of crowd coding, which allows a relatively fast manual coding of political texts. Some of the advantages of crowd coding are that it is easily replicated and expanded, and, as such, presents the research community with the opportunity to amend and expand upon this coding scheme.

### Links
https://ejpr.onlinelibrary.wiley.com/doi/epdf/10.1111/1475-6765.12266
https://manifesto-project.wzb.eu/information/documents/pimpo

```{r}
library(readr)
library(dplyr)
library(ggplot2)
```

```{r}
PIM <- read_csv("../../PImPo dataset/PImPo_verbatim.csv")
```

```{r}
PIM %>% filter(selection=="1",manually_coded==FALSE) -> data

contries <- c("sweden","norway","denmank","finland","netherlands","spain","germany","austria","switzerland","ireland","usa","canada","australia","new zealand")
countryCodes <- unique(data$country)

for (i in 1:14){
  data[data$country==countryCodes[i],"countryName"] = contries[i]
}

data[data$direction=="1","stance"]<-"Pro"
data[data$direction=="0","stance"]<-"Neutral"
data[data$direction=="-1","stance"]<-"Against"
```

```{r}
ggplot(data=data, aes(x=countryName)) +
  geom_bar() +
  geom_text(stat='count', aes(label=..count..), vjust=-1)

pie(table(data$topic),labels = c("immigration","integration"),main="topic distribution - whole dataset")

pie( table( filter(data,topic=="1") %>% select(direction)),labels = c("against","neutral","pro"),main = "Stance against immigration - whole dataset")

pie( table( filter(data,topic=="2") %>% select(direction)),labels = c("against","neutral","pro"),main = "Stance against integration - whole dataset")

pie(table( filter(data,country=="22") %>% select(party)),labels = c("green left","socialist party","labour party","d66","VVD","christian democrat appeal","christian union","party of freedom","party of the animals","reformed political party"),main = "dutch parties")

pie(table(data$stance),main = "stance distribution - whole dataset")
```

```{r}
toExport <- data[,c("countryName","party","content","topic","stance")]
```

```{r}
parties <- c("swe: Green Ecology Party","swe: Social Democratic Labour Party","swe: Liberal People’s Party","swe: Left Communists Party","swe: Christian Democratic Community Party ","swe: Moderate Coalition Party","swe: Sweden Democrats","swe: Centre Party","nor: Socialist Left Party","nor: Norwegian Labour Party","nor: Liberal Party","nor: Christian People’s Party","nor: Conservative Party","nor: Centre Party","nor: Progress Party","dnk: Liberal Alliance","dnk: Red-Green Unity List","dnk: Socialist People’s Party","dnk: Social Democratic Party","dnk: Centre Democrats","dnk: Radical Party","dnk: Liberals","dnk: Christian People’s Party","dnk: Conservative People’s Party","dnk: Danish People’s Party","dnk: Progress Party","fin: Green Union","fin: Left Wing Alliance","fin: Finnish Social Democrats","fin: Christian Democrats in Finland","fin: National Coalition","fin: Finnish Centre","fin: Finnish Rural Party","fin: Swedish People’s Party","nld: Green Left","nld: Socialist Party","nld: Labour Party","nld: Democrats‘66","nld: People’s Party for Freedom and Democracy ","nld: Christian Democratic Appeal","nld: Christian Union","nld: Party of Freedom","nld: Party for the Animals","nld: Reformed Political Party","esp: Future Yes","esp: Amaiur","esp: Commitment-Q","esp: United Left","esp: Spanish Socialist Workers’ Party","esp: Union, Progress and Democracy","esp: Popular Party","esp: Convergence and Union","esp: Forum Asturias","esp: Basque Nationalist Party","esp: Basque Solidarity","esp: Canarian Coalition","esp: Aragonist Council","deu: Alliance‘90/Greens","deu: Party of Democratic Socialism","deu: The Left","deu: Social Democratic Party of Germany","deu: Free Democratic Party","deu: Christian Democratic Union/C.Social Union ","aut: The Greens","aut: The Greens","aut: The Greens","aut: The Greens","aut: Austrian Communist Party","aut: Austrian Social Democratic Party","aut: Austrian Social Democratic Party","aut: Austrian Social Democratic Party","aut: Austrian Social Democratic Party","aut: Austrian Freedom Party","aut: Austrian Freedom Party","aut: Austrian Freedom Party","aut: Austrian Freedom Party","aut: Austrian People’s Party","aut: Austrian People’s Party","aut: Austrian People’s Party","aut: Austrian People’s Party","aut: Alliance for the Future of Austria","aut: Alliance for the Future of Austria","che: Green Party of Switzerland","che: Green Liberal Party","che: Swiss Labour Party","che: Social Democratic Party of Switzerland ","che: Radical Democratic Party","che: Conservative Christian Social Party","che: Protestant People’s Party of Switzerland ","che: Christian Social Party","che: Federal Democratic Union","che: Swiss People’s Party","che: Conservative Democratic Party of Switzer. ","irl: United Left Alliance","irl: Green Party","irl: Socialist Party","irl: Labour Party","irl: Progressive Democrats","irl: Familiy of the Irish","irl: Soldiers of Destiny","irl: Ourselves Alone","usa: Democratic Party","usa: Republican Party","can: Green Party","can: New Democratic Party","can: Liberal Party of Canada","can: Conservative Party of Canada","can: Quebec Bloc","aus: Australian Greens","aus: Australian Labor Party","aus: Palmer United Party","aus: Liberal Party of Australia","aus: Katter's Australian Party","aus: National Country Party","nzl: Green Party of Aotearoa New Zealand","nzl: New Zealand Labour Party","nzl: ACT New Zealand","nzl: United Future New Zealand","nzl: Progressive Party","nzl: New Zealand National Party","nzl: New Zealand First Party","nzl: Maori Party","nzl: Mana Party")

partyCodes <- c("11110","11320","11420","11220","11520","11620","11710","11810","12221","12320","12420","12520","12620","12810","12951","13001","13229","13230","13320","13330","13410","13420","13520","13620","13720","13951","14110","14223","14320","14520","14620","14810","14820","14901","22110","22220","22320","22330","22420","22521","22526","22722","22951","22952","33091","33092","33093","33220","33320","33440","33610","33611","33612","33902","33903","33907","33909","41113","41221","41223","41320","41420","41521","42110","42110","42110","42110","42220","42320","42320","42320","42320","42420","42420","42420","42420","42520","42520","42520","42520","42710","42710","43110","43120","43220","43320","43420","43520","43530","43540","43711","43810","43811","53021","53110","53230","53320","53420","53520","53620","53951","61320","61620","62110","62320","62420","62623","62901","63110","63320","63410","63620","63710","63810","64110","64320","64420","64421","64422","64620","64621","64901","64902")

partyMapping <- cbind(parties,partyCodes)
```

```{r}
partyMapping<-unique(partyMapping)

for (i in partyMapping[,2]){
  toExport[toExport$party == i,6] <- partyMapping[partyMapping[,2]==i,1]
}

colnames(toExport) <- c("country","partyCode","content","target","stance","party")
```

```{r}
toExport$target <- as.character(toExport$target)
toExport[toExport$target=="1",4]="Immigration"
toExport[toExport$target=="2",4]="Integration"

toExport[toExport$stance=="Pro",5]="FAVOR"
toExport[toExport$stance=="Against",5]="AGAINST"
toExport[toExport$stance=="Neutral",5]="NONE"

toExport <- select(toExport, country, party, content, target, stance)
```
```{r}
write.csv2(toExport,"PImPo.csv")
```

}
